Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-06 paper/main.tex
Update
Updates

\begin{figure}[t!]
    \begin{subfigure}{0.25 \textwidth}
	\centering
    	\includegraphics[page=1]{figures_v2.pdf}
    	\caption{$ N = 400 $}
    \end{subfigure}
    \begin{subfigure}{0.25\textwidth}
    	\includegraphics[page=2]{figures_v2.pdf}
    	\caption{ $ N = 800$ }
    \end{subfigure}
    \begin{subfigure}{0.25 \textwidth}
    	\includegraphics[page=3]{figures_v2.pdf}
    	\caption{ $ N = 400$ }
    \end{subfigure}%
    \begin{subfigure}{0.25\textwidth}
    	\includegraphics[page=4]{figures_v2.pdf}
    	\caption{$ N = 800$ }
    \end{subfigure}

@@

\begin{enumerate}
	\item \textbf{Bounded: } The measure is bounded between $ 0 $ (no
		association) to $ 1 $ (perfect linear association), simplifying
		interpretation.
	% \item \textbf{Independent of Sample Size: } 
	\item \textbf{Invariant to the Dummy Encoding: } For categorical
		variables, residuals are computed using dummy encoding. Since
		canonical correlations identifies linear combinations across
		columns, this measure is invariant to the specific dummy
		encoding scheme used.
	\item \textbf{Equivalent to Partial Correlation for Continuous Variables: }
		When both $ X $ and $ Y $ are continuous variables, our measure
		is equivalent to the absolute value of partial correlation coefficient.
	\item \textbf{Equivalent to polychoric and polyserial correlation for
			ordinal and continuous variables: }
		Under the assumption that the ordinal variable is generated by
		discretizing an underlying gaussian continuous variable, this
		effect size is equivalent to polychoric and polyserial
		correlation. As both of them recover the Pearson correlation
		coefficient.
	\item \textbf{Related to Cram\'er's V: } 
\end{enumerate}

@@

\section{Using Measure of Association for DAG Construction}
\label{sec:modification}

>>>>

\begin{figure}[t!]
    \begin{subfigure}{0.5 \textwidth}
	\centering
    	\includegraphics[page=1]{figures_v2.pdf}
    	\caption{PC algorithm with mutual information test. Red edges: $ N=400 $, Blue edges: $ N=800 $}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
    	\includegraphics[page=2]{figures_v2.pdf}
    	\caption{PC algorithm with a residualization based test. Red edges $N=400$, Blue edges: $ N=800 $}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
    	\includegraphics[page=3]{figures_v2.pdf}
    	\caption{PC algorithm with Hill Climb Search with BIC score}
    \end{subfigure}

@@

\begin{enumerate}
	\item \textbf{Bounded: } The measure is bounded between $ 0 $ (no
		association) to $ 1 $ (perfect linear association), simplifying
		interpretation.
	% \item \textbf{Independent of Sample Size: } 
	\item \textbf{Invariant to the Dummy Encoding: } For categorical
		variables, residuals are computed using dummy encoding. Since
		canonical correlations identifies linear combinations across
		columns, this measure is invariant to the specific dummy
		encoding scheme used.
	\item \textbf{Equivalent to Partial Correlation for Continuous Variables: }
		When both $ X $ and $ Y $ are continuous variables, our measure
		is equivalent to the absolute value of partial correlation coefficient.
	\item \textbf{Equivalent to polychoric and polyserial correlation for
			ordinal and continuous variables: }
		Under the assumption that the ordinal variable is generated by
		discretizing an underlying gaussian continuous variable, this
		effect size is equivalent to polychoric and polyserial
		correlation. As both of them recover the Pearson correlation
		coefficient.
		\todo[inline]{Verify if this is correct}
	\item \textbf{Related to Cram\'er's V: } 
\end{enumerate}

@@

\section{Using Measure of Association for Ranking and DAG Construction}
\label{sec:modification}
